Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-06-21 paper/paper.tex
Working on amplitude modulation

%\title{Dispersion of short waves riding on longer waves}
\title{Revisiting the linear theory of hydrodynamic wave modulation}

@@

TODO amplitude modulation;
The modulation of short-wave amplitude can be derived in the same way by
dropping the non-linear terms in the wave action balance equation
(Eq. \ref{eq:wave_action2}) and integrating wave action in time:

@@

\begin{equation}
\label{eq:wave_amplitude_modulation}
\widetilde{a}(\psi) = a \sqrt{
  \dfrac{g}{\widetilde{g}}
  \dfrac{\sigma}{\widetilde{\sigma}}
  \dfrac{\widetilde{N}}{N}}
\end{equation}
To determine $\widetilde{\sigma}$, we will need to evaluate the modulation of
the gravitational acceleration at the surface of the long wave.

>>>>

%\title{Dispersion of short waves riding on longer waves}
\title{Revisiting the hydrodynamic wave modulation from linear wave theory}

@@

The modulation of short-wave amplitude can be derived in the same way by
dropping the non-linear terms in the wave action balance equation
(Eq. \ref{eq:wave_action2}) and integrating wave action in time:

@@

\begin{equation}
\label{eq:wave_amplitude_modulation}
\widetilde{a}(\psi) = a \sqrt{
  \dfrac{g}{\widetilde{g}}
  \dfrac{\sigma}{\widetilde{\sigma}}
  \dfrac{\widetilde{N}}{N}}
=
  \left( \dfrac{\widetilde{g}}{g} \right)^{0.75}
  \left( \dfrac{\widetilde{k}}{k} \right)^{0.25}
  \left( \dfrac{\widetilde{N}}{N} \right)^{0.5}
\end{equation}
To the 1$^{st}$ order in $\varepsilon_L$, the amplitude modulation is then:

\begin{equation}
\label{eq:wave_amplitude_modulation_order1}
\dfrac{\widetilde{a}}{a} = 
  \left( \dfrac{\widetilde{g}}{g} \right)^{0.75}
  \left( 1 + \varepsilon_L \right)^{0.75}
\end{equation}

To determine $\widetilde{\sigma}$, we will need to evaluate the modulation of
the gravitational acceleration at the surface of the long wave.
